---
title: "requirements"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  # Figures (http://r4ds.had.co.nz/)
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  fig.asp = 0.618,
  fig.show = "hold"
)
```

FIXME 

* `rtbl()` should not output missing values of `censusid` (https://github.com/forestgeo/rtbl/issues/53).


---

```
From: Lao, Suzanne
Sent: Tuesday, April 30, 2019 2:47 PM
To: Lepore, Mauro <LeporeM@si.edu>; Shameema Jafferjee Esufali (shameemaesufali@gmail.com)
<shameemaesufali@gmail.com>
Cc: Krizel, Lauren <KrizelL@si.edu>
Subject: RE: Building R stem tables for the upcomming workshop
```

> When making the R stem tables, please note the following comments when determining the status variable.

1. DFstatus is exactly the same as the status variable in ViewFullTable.

2. The status variable in the R tables is calculated as follows for stems:

```{r, echo=FALSE}
status_in_viewfulltable <- c("alive", "dead", "broken below or stem dead", "missing")
status_after_rtbl <- c("A", "D", "G", "M")
knitr::kable(tibble::tibble(status_in_viewfulltable, status_after_rtbl))
```

> Also, do the following:

3. Give an Rstatus of P -"prior", if a stem does not appear in the first censuses, i.e. stem is first measured in a later census.

Propagate `status == P` forward in all censuses until it first appears.

4. Propagate the Rstatus D (dead) forward, even if the stem disappears in later censuses.

5. G - "gone" - propagate forward (even if stem disappears in later censuses) until the stem is measured again in a later census.

6. If a stem was dead in a census, then later found alive, go back and change all the Rstatus 'D' to 'A'.

> Stems may go through the following Rstatuses and in this order:

`P (prior) -> A (alive) -> G (gone) -> D (dead)`

P, G, and/or D may be missing.

> Problems that have to be fixed in the Rstatus sequence:

7. P should NEVER follow any of the other Rstatuses. It should be the first Rstatus, or not appear at all.

8. P should not go directly to G or D, without first going to A.

9. D should never be followed by A or G.

10. Stems should not start with a G, they should start with P or A. Somemes they start with a D when the site tags and measures dead stems

> The folder called "onecensus" contains the data from sites for which I have one census only. You may not need to make R tables for these sites, since the R tables that already exist should be fine. You may still want to make them to compare with those that are on the server.

